
## STEP 0: LOAD THE LIBRARIES
```{r}
library(caret)
library(rpart)
library(rpart.plot)
library(randomForest)
library(corrplot)
```

## STEP 1: LOAD THE TRAINING AND TEST DATA
```{r}
trainRaw = read.csv("./data/pml-training.csv")
testRaw = read.csv("./data/pml-testing.csv")
dim(trainRaw)
dim(testRaw)
```

## STEP 2: UNDERSTAND THE PROBLEM: THE GOAL IS TO PREDICT THE MANNER IN WHICH THEY DID EXERCIES - "classe" variable
```{r}
str(trainRaw$classe)
```

## STEP 3: DATA CLEANING EXERCISE
```{r}
trainRaw = trainRaw[, colSums(is.na(trainRaw)) == 0] # RETAIN COLUMNS WITHOUT NAs
testRaw = testRaw[, colSums(is.na(testRaw)) == 0] # RETAIN COLUMNS WITHOUT NAs
classe = trainRaw$classe
trainRaw = trainRaw[,-c(1,3,4,5,6,7)]
trainOnlyNum = trainRaw[, sapply(trainRaw, is.numeric)] #RETAIN NUMERIC COLUMNS
trainOnlyNum$classe = classe # THIS IS A FACTOR WE ARE TRYING TO PREDICT

testRaw = testRaw[,-c(1,3,4,5,6,7)]
testOnlyNum = testRaw[, sapply(testRaw, is.numeric)]
```

## STEP 4: MODEL USING RANDOM FOREST - USE 70:30 FOR CROSS-VALIDATION
```{r}
set.seed(1000) # For reproducibile purpose
inTrain = createDataPartition(trainOnlyNum$classe, p = 0.70, list = F)
trainData = trainOnlyNum[inTrain,]
testData = trainOnlyNum[-inTrain,]
controlRf <- trainControl(method = "cv", 5)
modelRf <-
	train(
		classe ~ .,
		data = trainData,
		method = "rf",
		trControl = controlRf,
		ntree = 250
	)

```

## STEP 5: PREDICT USING THE TRAIN DATA
```{r}
predictRf = predict(modelRf, testData)
```

## STEP 6: FIND THE ACCURACY WITH OUT-SAMPLE DATA
```{r}
confusionMatrix(testData$classe, predictRf)
confusionMatrix(testData$classe, predictRf)$overall[1]
accuracy = postResample(predictRf, testData$classe)
accuracy
outOfSampleError =	1 - as.numeric(confusionMatrix(testData$classe, predictRf)$overall[1])
outOfSampleError
result =	predict(modelRf, testOnlyNum[,-length(names(testOnlyNum))])
result
```

## STEP 7: DESCRIPTIVE PLOT - CORRELATION BETWEEN PREDICTORS; TREE MODEL OUPUT
```{r}
corrPlot = cor(trainData[,-length(names(trainData))])
corrplot(corrPlot, method = "circle")
treeModel = rpart(classe ~ ., data = trainData, method = "class")
prp(treeModel) # fast plot
```